A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Remove VC description in digital identity

\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

\begin{table}[h]
	\caption{The comparison of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabularx}
\end{table}

@@

In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata. The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments. If a VC is verified via issuer's public key, the message will be labelled as trusted. Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.in]{DID_VC}
    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
    \label{fig:did_vc}
\end{figure}

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.

>>>>

\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
\begin{table}[h]
	\caption{Identity models: centralized vs. decentralized}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabularx}
\end{table}

@@

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.
